Comparing software variability across and within fMRI analysis packages

### 2022-02-21 paper/paper.tex
Update results

\begin{equation}
  N = (-1)^s \times 2^E \times (1.m),
\end{equation}
where $E=e-127$ for single precision and $E=e-1023$ for double precision.
In single precision, the pseudo-mantissa has 23 bits and the exponent has 8 bits, whereas in
double precision the pseudo-mantissa has 52 bits and the exponent has 11 bits.
Machine error, the smallest absolute difference between two
floating-point numbers that can be represented, is in general $2^{-24}\times e$ in
single precision and $2^{-53}\times e$ in double precision.
We simulated machine error by introducing the random perturbation defined
in Equation~\ref{eq:mca_inexact} at the virtual precision of $t=24$~bits for single-precision
values and $t=53$~bits for double-precision ones. The perturbed pseudo-mantissa
is obtained by extending the size of the original pseudo-mantissa, applying the perturbation
at the desired virtual precision, and rounding the perturbed result back to the original precision.
We simulated within-tool software variability (WT) by running the same analyses three
times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
double-precision values and $t=24$~bits for single-precision values. 
Perturbations were applied at the same magnitude of floating-point precisions during the pipeline execution
regardless of what it corresponds to.
These values were chosen such that the numerical perturbation affects all the pipeline steps and simulates
machine error originating from software, hardware, and operating system changes.
The resulting samples are equally plausible estimates of
the true numerical result at the precision used by the pipelines.

We evaluated BT for thresholded as well as unthresholded
group-level and subject-level t-statistic maps by computing the
differences of t-statistic maps across tools. For WT, we computed the
average difference across the three Fuzzy Libmath samples.
Moreover, we computed WT variability for a pair of tools as the sum of WT absolute differences for each tool.
All differences were computed over the intersection of t-statistic maps between the pair of tools.

@@

Table~\ref{table:pipeline-stats} presents summary statistics for variability in the
group-level t-statistic. 
Mean of differences in t-statistic maps is generally centered around zero for BT and WT
(one-sample t-test p~\textless~$10^{-4}$ for all tests).
However, for each tool pair (A, B), BT variability was
significantly larger than machine error in tool A or B,
with an order of magnitude larger standard deviation of differences 
in both thresholded and unthresholded maps, 
(Wilcoxon signed-rank test and t-test p~\textless~$10^{-4}$ for all tests).
These global differences were confirmed by Bland-Altman plots showing a
clear dominance of BT over WT
(Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B}).
In addition, BT and WT appeared moderately correlated across voxels (Pearson's r
in [0.68, 0.69], p$< 10^{-5}$, Figure~\ref{fig:unthresh-maps}-\textbf{C}). 
% Interestingly, the correlation appears driven by a set of voxels exhibiting comparable BT and
% WT values located around the identity line in Figure~\ref{fig:unthresh-maps}D, which, however, did not seem to have
% any spatial consistency.

\setlength{\tabcolsep}{5pt}
\begin{table}[h]
  \centering
  \begin{tabular}{cccccc|cc}
    \toprule
                      &              & \multicolumn{4}{c|}{Group map}  & \multicolumn{2}{c}{Subject maps}                                                                     \\
    \multirow{2}{*}{} & {}           & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded}                               \\
    % \cmidrule{3-8}
    {}                & {}           & $\mu$                           & $\sigma$                           & $\mu$                             & $\sigma$ & $\mu$ & $\sigma$ \\
    \midrule
    \rowcolor{lightgray!50}
    {Between Tools}   & FSL vs. SPM  & -0.668                           & 1.056                              & -0.033                             & 1.121    & 0.068 & 0.937    \\
    \rowcolor{lightgray!50}
    {(BT)}            & FSL vs. AFNI & -0.823                           & 1.857                              & 0.048                             & 1.439    & 0.034 & 1.146    \\
    \rowcolor{lightgray!50}
    {}                & AFNI vs. SPM & 0.645                           & 1.428                              & 0.064                             & 1.489    & -0.065 & 1.206    \\
    {Within Tool}     & FSL          & -0.003                           & 0.069                              & -0.010                             & 0.103    & -0.002 & 0.099    \\
    {(WT)}            & SPM          & 0.001                           & 0.097                              & 0.000                             & 0.076    & 0.000 & 0.064    \\
    {}                & AFNI         & 0.002                           & 0.228                              & -0.001                             & 0.178    & 0.000 & 0.178    \\
    \bottomrule
  \end{tabular}
  \caption{Voxel-wise mean and standard deviation of BT and WT variability in t-statistic maps.}
  \label{table:pipeline-stats}
\end{table}

\begin{figure*}[ht]
  \centering
  % \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  \begin{subfigure}[ht]{.9\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{figures/gl-unthresh.png}
    % \includegraphics[width=0.9\textwidth]{figures/abs/gl-unthresh.png}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
  \end{subfigure}
  \caption{\textbf{A} and \textbf{B}: Bland-Altman plots comparing group-level differences computed between tools
    (\textbf{A}) and within tools at machine error (\textbf{B}). \textbf{C}: voxel-wise comparison of absolute differences.}
  \label{fig:unthresh-maps}
  % \end{minipage}}
\end{figure*}

@@

Table~\ref{table:pipeline-stats} also presents summary statistics for
subject-level unthresholded t-statistic maps (mean over subjects).
As for group-level maps, BT was consistently larger than WT (Wilcoxon
signed-rank test and t-test p~\textless~$10^{-4}$ for 12 subjects).
However, for some subjects and for AFNI, WT approached 
BT in some regions (Figure~\ref{fig:unthresh-maps-sbj}). As for the group maps, BT and WT
 appeared moderately correlated for all subjects (r in [0.52,
    0.69], p$< 10^{-5}$ for all subjects, see Supplemental Material~\ref{sec:supp-subjects} and~\ref{sec:supp-worst-subject}).

%%%%%%%%%% Var. of Unthresh sbj05%%%%%%%%
\begin{figure*}[ht]
  \centering
  \includegraphics[width=0.9\textwidth]{figures/plots/Bland-Altman/unthresh-sbj10.png}
  % \includegraphics[width=0.9\textwidth]{figures/abs/sbj05-abs.png}
  %\caption{Standard deviation of thresholded t-statistics map on template surface}
  \caption{For subject with highest WT variability,
    unthresholded subject-level variability computed between tools (\textbf{A}), and within tools at machine error (\textbf{B}).}
    % and difference between them (\textbf{C}). \camille{If the changes are visible, I think that it would be useful to add the correspondant unthresholded maps for the reader to see where the differences are and what they "look like"}}
  \label{fig:unthresh-maps-sbj}
\end{figure*}

@@

Moreover, to compare the effects of BT and WT on the detection of activated
regions, we measured WT instability and BT instability in each region of
the HCP-MMP1.0 parcellation. The confusion matrices in
Figure~\ref{fig:thresh-maps}-\textbf{D} report these instabilities for the
360 tested regions. The average ratio of unstable regions was 26\% for BT
and 9.2\% for WT, which confirmed that BT was larger than
WT even in thresholded maps.

Finally, we measured agreement between BT and WT from the confusion
matrices since interpreting the correlation of thresholded maps is
difficult due to the discontinuity introduced by thresholding. 
The average Cohen's kappa score\footnote{$\kappa \leq 0$ denotes chance agreement, $-1 \leq \kappa \leq 1$}
computed from the confusion matrices between WT instability and BT instability was $\kappa=0.17$, indicating
a moderate agreement between WT instability and BT instability consistent with the correlations observed in 
unthresholded maps.

@@

%%%%%%%%%% Var. of Thresh %%%%%%%%
\begin{figure*}[ht]
  \begin{subfigure}[ht]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/act_deact-marked.pdf}
    % \includegraphics[width=\textwidth]{figures/plots/wt-tstats/act_deact-framed.png}
    % \includegraphics[width=\textwidth]{figures/abs/gl-thresh.png}
    %\caption{Standard deviation of thresholded t-statistics map on template surface}
  \end{subfigure}
  \centering
  \caption{\textbf{A},\textbf{B},\textbf{C}: Thresholded group-level
    t-statistic within tools at machine error for FSL (\textbf{A}), SPM
    (\textbf{B}) and AFNI (\textbf{C}). Arrows point to activation clusters
    impacted by both within- and between-tool variability.
     \textbf{D}: Confusion matrices of
    activation instability in BT and WT among the 360 regions of the
    HCP-MMP1.0 parcellation.}
  \label{fig:thresh-maps}
\end{figure*}

@@

In fMRI group analyses, within-tool software variability remains an order
of magnitude smaller than between-tool variability. This is likely
explained by the fact that group analyses benefit from regularization of
numerical noise, which is expected to increase with sample size. This finding is
consistent with observations made in~\cite{kiar2020numerical} from
diffusion MRI data where connectome graph statistics were found to be
substantially unstable at the subject level while group distributions
remained consistent. Therefore,
for fMRI studies with large sample sizes, within-tool software variability
may be neglected with respect to between-tool variability. In particular,
multiverse analyses aggregating the outcome of multiple analysis tools are
likely to successfully correct for machine error in such group studies.  Nevertheless, within-tool software variability remains
substantial in group analyses that are based on a single tool, as is
commonly the case in current fMRI studies. In particular, in our study, the
inherent instability of thresholding was triggered by within-tool software
variability in 9\% of 360 brain regions, which indicates that it might have
impacted neuroscientific conclusions related to these regions.

In subject-level analyses, within- and between-tool software variabilties can become
of comparable magnitude for some subjects in some regions. This observation
can be used as a proxy for data quality, and
is particularly relevant to the development of fMRI-based biomarkers aiming
at individualized phenotype predictions. Machine error may play
a non-negligible role in such analyses, even when predictions combine
results produced by multiple tools.

@@

\section{BT and WT correlations for all subjects}
\label{sec:supp-subjects}

Figure~\ref{fig:unthresh-correlation-allsbj} plots the relationship between
WT and BT for each subject across voxels, showing a consistent moderate correlation between BT and
WT.

\begin{figure*}[ht]
  \centering
  \includegraphics[width=.55\textwidth]{figures/sbj-abs-corr-unthresh-plot.png}
  % \includegraphics[width=.6\textwidth]{figures/sbj-abs-corr-unthresh-plot.png}
  \caption{Comparison between BT and WT variabilty for 16 subjects.}
  \label{fig:unthresh-correlation-allsbj}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/10-marked.pdf}
  % \includegraphics[width=\textwidth]{figures/plots/wt-tstats/5-framed.png}
  % \includegraphics[width=.6\textwidth]{figures/sbj-abs-corr-unthresh-plot.png}
  \caption{For subject with highest WT variability, unthresholded subject-level t-statistic
  within tools at machine error for FSL (\textbf{A}),
  SPM (\textbf{B}), AFNI (\textbf{C}).}% \camille{If I understand correctly the point you are making here is that WT(AFNI) at some voxels is close to AFNI-SPM ? What is surprising here for me is that WT(AFNI) seems to be quite different from WT(SPM) and WT(FSL). Do we have a good idea why? Maybe looking at the maps would help?}
  %\ali{We are pointing regions with instability in both WT and BT, and yes indeed it shows a very different WT(AFNI) compare to WT(FSL) and WT(SPM), but we did not investigate the reason of variabilities for now.} }
  \label{fig:unthresh-worst-sbj}
\end{figure*}

>>>>

\begin{equation}
  N = (-1)^s \times 2^E \times (1.m),
\end{equation}
where $E=e-127$ for single precision and $E=e-1023$ for double precision.
In single precision, the pseudo-mantissa has 23 bits and the exponent has 8 bits, whereas in
double precision the pseudo-mantissa has 52 bits and the exponent has 11 bits.
Machine error, the smallest absolute difference between two
floating-point numbers that can be represented, is in general $2^{-24}\times e$ in
single precision and $2^{-53}\times e$ in double precision.
We simulated machine error by introducing the random perturbation defined
in Equation~\ref{eq:mca_inexact} at the virtual precision of $t=24$~bits for single-precision
values and $t=53$~bits for double-precision ones. The perturbed pseudo-mantissa
is obtained by extending the size of the original pseudo-mantissa, applying the perturbation
at the desired virtual precision, and rounding the perturbed result back to the original precision.
We simulated within-tool software variability (WT) by running the same analyses 10
times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
double-precision values and $t=24$~bits for single-precision values. 
Perturbations were applied at the same magnitude of floating-point precisions during the pipeline execution
regardless of what it corresponds to.
These values were chosen such that the numerical perturbation affects all the pipeline steps and simulates
machine error originating from software, hardware, and operating system changes.
The resulting samples are equally plausible estimates of
the true numerical result at the precision used by the pipelines.

We evaluated BT for thresholded as well as unthresholded
group-level and subject-level t-statistic maps by computing the
differences of t-statistic maps across tools. For WT, we computed the
average difference across the 10 Fuzzy Libmath samples.
% Moreover, we computed WT variability for a pair of tools as the sum of WT absolute differences for each tool.
% All differences were computed over the intersection of t-statistic maps between the pair of tools.

@@

Table~\ref{table:pipeline-stats} presents summary statistics for variability in the
group-level t-statistic.
Mean of differences in t-statistic maps is centered around zero for BT and WT
in both thresholded and unthresholded maps (t-test p~\textless~$10^{-5}$).
However, for each tool pair (A, B), BT variability was
significantly larger than WT in tool A or B,
with an order of magnitude larger standard deviation of differences 
in both thresholded and unthresholded maps, 
(Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$).
These global differences were confirmed by Bland-Altman plots showing a
clear dominance of BT over WT
(Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B}).
In addition, results show that BT and WT were not correlated across voxels
(Pearson's r $\approx 0$, p$< 10^{-5}$, Figure~\ref{fig:unthresh-maps-corr}).
% Interestingly, the correlation appears driven by a set of voxels exhibiting comparable BT and
% WT values located around the identity line in Figure~\ref{fig:unthresh-maps}D, which, however, did not seem to have
% any spatial consistency.

\setlength{\tabcolsep}{5pt}
\begin{table}[h]
  \centering
  \begin{tabular}{cccccc|cc}
    \toprule
                      &              & \multicolumn{4}{c|}{Group map}  & \multicolumn{2}{c}{Subject maps}                                                                     \\
    \multirow{2}{*}{} & {}           & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded}                               \\
    % \cmidrule{3-8}
    {}                & {}           & $\mu$                           & $\sigma$                           & $\mu$                             & $\sigma$ & $\mu$ & $\sigma$ \\
    \midrule
    \rowcolor{lightgray!50}
    {Between Tools}   & FSL vs. SPM  & -0.845                           & 2.639                              & -0.052                             & 1.122    & -0.059 & 0.911    \\
    \rowcolor{lightgray!50}
    {(BT)}            & FSL vs. AFNI & -0.871                           & 3.216                              & 0.048                             & 1.405    & -0.027 & 1.097    \\
    \rowcolor{lightgray!50}
    {}                & AFNI vs. SPM & 0.426                           & 3.214                              & -0.113                             & 1.543    & -0.104 & 1.208    \\
    {Within Tool}     & FSL          & -0.009                           & 0.266                              & 0.012                             & 0.046    & 0.004 & 0.042    \\
    {(WT)}            & SPM          & 0.000                           & 0.199                              & 0.000                             & 0.035    & 0.000 & 0.029    \\
    {}                & AFNI         & -0.004                           & 0.273                              & 0.000                             & 0.084    & 0.000 & 0.075    \\
    \bottomrule
  \end{tabular}
  \caption{Voxel-wise mean and standard deviation of BT and WT variability in t-statistic maps.}
  \label{table:pipeline-stats}
\end{table}

\begin{figure*}[ht]
  \centering
    \includegraphics[width=.9\textwidth]{figures/plots/Bland-Altman/with-masking/unthresh-gl-frame.png}
  \caption{\textbf{A} and \textbf{B}: Bland-Altman plots comparing group-level differences computed between tools
    (\textbf{A}) and within tools at machine error (\textbf{B}).}% \textbf{C}: voxel-wise comparison of absolute differences.}
  \label{fig:unthresh-maps}
\end{figure*}

\begin{figure*}[ht]
  \centering
  \includegraphics[width=.9\textwidth]{figures/rel-corr-unthresh-with-masking.png}
  \caption{Voxel-wise comparison of group-level differences in BT and WT.}
  \label{fig:unthresh-maps-corr}
\end{figure*}

@@

Table~\ref{table:pipeline-stats} also presents summary statistics for
subject-level unthresholded t-statistic maps (mean over subjects).
As for group-level maps, BT was consistently larger than WT (Wilcoxon
signed-rank test and t-test p~\textless~$10^{-4}$ for 14 subjects).
However, for some subjects and for AFNI, WT approached 
BT in some regions (Figure~\ref{fig:unthresh-maps-sbj},
and see Supplemental Material~\ref{sec:supp-worst-subject}).
% As for the group maps, BT and WT
% showed no correlation across voxels for all subjects
% (r$\approx 0$, p$< 10^{-5}$ for all subjects, see Supplemental Material~\ref{sec:supp-subjects} and~\ref{sec:supp-worst-subject}).

%%%%%%%%%% Var. of Unthresh sbj05%%%%%%%%
\begin{figure*}[ht]
  \centering
  \includegraphics[width=0.9\textwidth]{figures/plots/Bland-Altman/with-masking/unthresh-sbj04.png}
  \caption{For subject with highest WT variability,
    unthresholded subject-level variability computed between tools (\textbf{A}), and within tools at machine error (\textbf{B}).}
    % and difference between them (\textbf{C}). \camille{If the changes are visible, I think that it would be useful to add the correspondant unthresholded maps for the reader to see where the differences are and what they "look like"}}
  \label{fig:unthresh-maps-sbj}
\end{figure*}

@@

Moreover, to compare the effects of BT and WT on the detection of activated
regions, we measured WT instability and BT instability in each region of
the HCP-MMP1.0 parcellation. The confusion matrices in
Figure~\ref{fig:thresh-maps}-\textbf{D} report these instabilities for the
360 tested regions. The average ratio of unstable regions was 26.2\% for BT
and 20.6\% for WT, which confirmed that BT was larger than
WT even in thresholded maps.

Finally, we measured agreement between BT and WT from the confusion
matrices since interpreting the correlation of thresholded maps is
difficult due to the discontinuity introduced by thresholding. 
The average Cohen's kappa score\footnote{$\kappa \leq 0$ denotes chance agreement, $-1 \leq \kappa \leq 1$}
computed from the confusion matrices between WT instability and BT instability was $\kappa=0.2$, indicating
a moderate agreement between WT instability and BT instability consistent with the correlations observed in 
unthresholded maps.

@@

%%%%%%%%%% Var. of Thresh %%%%%%%%
\begin{figure*}[ht]
  \begin{subfigure}[ht]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/act_deact-marked.pdf}
  \end{subfigure}
  \centering
  \caption{\textbf{A},\textbf{B},\textbf{C}: Thresholded group-level
    t-statistic within tools at machine error for FSL (\textbf{A}), SPM
    (\textbf{B}) and AFNI (\textbf{C}). Arrows point to activation clusters
    impacted by both within- and between-tool variability.
     \textbf{D}: Confusion matrices of
    activation instability in BT and WT among the 360 regions of the
    HCP-MMP1.0 parcellation.(with masking)}
  \label{fig:thresh-maps}
\end{figure*}

\subsection{Brain masking instability was triggered by WT and BT}

While the previous results were obtained over the union of t-statistic maps between the pair of tools,
we also computed results in the intersection of maps and found that the brain masking instability was
triggered by both BT and WT.
BT and WT variabilities were consistently smaller than ones with the fixed masks
in both thresholded and unthresholded maps (see Table~\ref{table:pipeline-stats-fixed-mask}).
The effect of masking was clearly appeared in BT by Bland-Altman plots showing that blob lines
were removed after fixing masks (Figure~\ref{fig:unthresh-maps-mask}-\textbf{A},\textbf{B}).

%%%%%%%%%% Summary of statstics %%%%%%%%
\setlength{\tabcolsep}{5pt}
\begin{table}[h]
  \centering
  \begin{tabular}{cccccc|cc}
    \toprule
                      &              & \multicolumn{4}{c|}{Group map}  & \multicolumn{2}{c}{Subject maps}                                                                     \\
    \multirow{2}{*}{} & {}           & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded}                               \\
    % \cmidrule{3-8}
    {}                & {}           & $\mu$                           & $\sigma$                           & $\mu$                             & $\sigma$ & $\mu$ & $\sigma$ \\
    \midrule
    \rowcolor{lightgray!50}
    {Between Tools}   & FSL vs. SPM  & -0.668                           & 1.056                              & -0.033                             & 1.121    & -0.068 & 0.937    \\
    \rowcolor{lightgray!50}
    {(BT)}            & FSL vs. AFNI & -0.823                           & 1.857                              & 0.048                             & 1.439    & 0.034 & 1.146    \\
    \rowcolor{lightgray!50}
    {}                & AFNI vs. SPM & 0.645                           & 1.428                              & 0.064                             & 1.489    & -0.065 & 1.206    \\
    {Within Tool}     & FSL          & -0.025                           & 0.197                              & 0.012                             & 0.043    & 0.004 & 0.041    \\
    {(WT)}            & SPM          & -0.002                           & 0.154                              & 0.000                             & 0.033    & 0.000 & 0.028    \\
    {}                & AFNI         & -0.008                           & 0.208                              & 0.000                             & 0.078    & 0.000 & 0.072    \\
    \bottomrule
  \end{tabular}
  \caption{Voxel-wise mean and standard deviation of BT and WT variability in intersected t-statistic maps.}
  \label{table:pipeline-stats-fixed-mask}
\end{table}

\begin{figure*}[ht]
  \centering
    \includegraphics[width=.9\textwidth]{figures/plots/Bland-Altman/fixed-mask/unthresh-gl-frame.png}
  \caption{\textbf{A} and \textbf{B}: Bland-Altman plots comparing group-level differences computed over the intersections 
  between tools (\textbf{A}) and within tools at machine error (\textbf{B}).}% \textbf{C}: voxel-wise comparison of absolute differences.}
  \label{fig:unthresh-maps-mask}
\end{figure*}

@@

In fMRI group analyses, within-tool software variability remains an order
of magnitude smaller than between-tool variability. This is likely
explained by the fact that group analyses benefit from regularization of
numerical noise, which is expected to increase with sample size. This finding is
consistent with observations made in~\cite{kiar2020numerical} from
diffusion MRI data where connectome graph statistics were found to be
substantially unstable at the subject level while group distributions
remained consistent. Therefore,
for fMRI studies with large sample sizes, within-tool software variability
may be neglected with respect to between-tool variability. In particular,
multiverse analyses aggregating the outcome of multiple analysis tools are
likely to successfully correct for machine error in such group studies.  Nevertheless, within-tool software variability remains
substantial in group analyses that are based on a single tool, as is
commonly the case in current fMRI studies. In particular, in our study, the
inherent instability of thresholding was triggered by within-tool software
variability in 20\% of 360 brain regions, which indicates that it might have
impacted neuroscientific conclusions related to these regions.

In subject-level analyses, within- and between-tool software variabilities can become
of comparable magnitude for some subjects in some regions. This observation
% can be used as a proxy for data quality, and
is particularly relevant to the development of fMRI-based biomarkers aiming
at individualized phenotype predictions. Machine error may play
a non-negligible role in such analyses, even when predictions combine
results produced by multiple tools.

@@

% \section{BT and WT correlations for all subjects}
% \label{sec:supp-subjects}

% Figure~\ref{fig:unthresh-correlation-allsbj} plots the relationship between
% WT and BT for each subject across voxels, showing a consistent moderate correlation between BT and
% WT.

% \begin{figure*}[ht]
%   \centering
%   \includegraphics[width=.55\textwidth]{figures/sbj-abs-corr-unthresh-plot.png}
%   % \includegraphics[width=.6\textwidth]{figures/sbj-abs-corr-unthresh-plot.png}
%   \caption{Comparison between BT and WT variabilty for 16 subjects.}
%   \label{fig:unthresh-correlation-allsbj}
% \end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/4-marked.pdf}
  % \includegraphics[width=\textwidth]{figures/plots/wt-tstats/5-framed.png}
  % \includegraphics[width=.6\textwidth]{figures/sbj-abs-corr-unthresh-plot.png}
  \caption{For subject with highest WT variability, unthresholded subject-level t-statistic
  within tools at machine error for FSL (\textbf{A}),
  SPM (\textbf{B}), AFNI (\textbf{C}).}% \camille{If I understand correctly the point you are making here is that WT(AFNI) at some voxels is close to AFNI-SPM ? What is surprising here for me is that WT(AFNI) seems to be quite different from WT(SPM) and WT(FSL). Do we have a good idea why? Maybe looking at the maps would help?}
  %\ali{We are pointing regions with instability in both WT and BT, and yes indeed it shows a very different WT(AFNI) compare to WT(FSL) and WT(SPM), but we did not investigate the reason of variabilities for now.} }
  \label{fig:unthresh-worst-sbj}
\end{figure*}
